\documentclass[letterpaper,11pt]{article}

\usepackage[margin=0.4in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage[colorlinks=true, urlcolor={blue!70!black}, linkcolor={blue!70!black}]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\setlist[itemize]{
  noitemsep,
  topsep=0pt,
  partopsep=0pt,
  parsep=0pt,
  itemsep=0pt,
  leftmargin=1.2em
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{4pt}{2pt}

\pagestyle{empty}

\begin{document}

%--- Header ---%
\begin{center}
  {\LARGE\textbf{MIR YASEEN ALI}}\\[2pt]
  {
    \href{https://d3mte3hn7uzxb.cloudfront.net}{Portfolio} \textbar\
    (630) 331-6311 \textbar\
    \href{mailto:mir.yaseen29343@gmail.com}{mir.yaseen29343@gmail.com}
    \\
    \href{https://linkedin.com/in/yaseen0011}{linkedin.com/in/yaseen0011} \textbar\
    \href{https://github.com/Gogeta0011}{github.com/Gogeta0011} \textbar\
    U.S. Permanent Resident
  }
\end{center}

%--- Technical Skills ---%
\section{TECHNICAL SKILLS}
\textbf{Cloud \& Infrastructure:} AWS (S3, CloudFront, IAM), Linux (Ubuntu), TCP/IP, DNS, DHCP, Docker (familiar)\\
\textbf{DevOps \& CI/CD:} GitHub Actions, Git, Git workflows, Agile Scrum\\
\textbf{Programming Languages:} Python, Java, C, C++, SQL (MySQL), JavaScript, HTML/CSS\\
\textbf{Developer Tools:} VS Code, OpenCV, MediaPipe\\
\textbf{Concepts \& Protocols:} REST APIs, OAuth 2.0, Role-Based Access Control (RBAC), JWT, TLS, HTTPS, CRUD, MVC

%--- Certifications ---%
\section{CERTIFICATIONS}
\textbf{AWS Certified Cloud Practitioner} \href{https://www.credly.com/badges/338f9986-645d-4cdf-bdc5-0cd27b5a0535}{(verify)} \hfill Issued Jan 2026 -- Expires Jan 2029

%--- Engineering Projects ---%
\section{ENGINEERING PROJECTS}
\noindent\textbf{Cloud Portfolio Platform} \href{https://d3mte3hn7uzxb.cloudfront.net}{[website]} \href{https://github.com/Gogeta0011/Portfolio-Website}{[github]} \textbar\ AWS (S3, CloudFront, IAM), GitHub Actions, JavaScript \hfill January 2026
\begin{itemize}
  \item Deployed and maintained a cloud-hosted site on AWS using S3 and CloudFront, configuring infrastructure for high availability, consistent delivery, and secure access control.
  \item Automated deployment workflows using GitHub Actions, reducing manual steps and ensuring repeatable, reliable releases across updates.
  \item Enforced security best practices using Origin Access Control, scoped IAM bucket policies, HTTPS-only behavior, and billing alerts to monitor infrastructure costs.
\end{itemize}
\noindent\textbf{Secure File Management System} \href{https://github.com/Gogeta0011/Secure-File-Management}{[github]} \textbar\ Java, MySQL \hfill November 2025
\begin{itemize}
  \item Built a Java backend with role-based access control (RBAC) for multi-user file management, enforcing least-privilege permissions across read, upload, edit, and delete operations.
  \item Designed a normalized MySQL schema for users, roles, and file metadata with transaction-based updates to ensure data integrity and reliability under concurrent operations.
  \item Implemented input validation and authentication checks around sensitive actions to reduce attack surface and improve overall system security posture.
\end{itemize}
\noindent\textbf{Ice Cream Shop Analytics Dashboard} \href{https://github.com/Gogeta0011/Ice-Cream-Shop-Analytics-Dashboard}{[github]} \textbar\ JavaScript, HTML/CSS, Python \hfill March 2026
\begin{itemize}
  \item Built a full-stack web dashboard consolidating sales, inventory, and staffing data from multiple sources to surface business insights in a single view.
  \item Designed a data pipeline to ingest and normalize inputs from different formats, laying groundwork for predictive features such as next-day sales forecasting and staffing recommendations.
  \item Collaborated with a stakeholder throughout development to gather requirements, iterate on the UI, and align the solution to real operational needs.
\end{itemize}
\noindent\textbf{GmailBillTracker} \href{https://github.com/Gogeta0011/GmailBillTracker}{[github]} \textbar\ Python, Gmail API, OAuth 2.0 \hfill August 2025
\begin{itemize}
  \item Automated processing of 100+ emails via the Gmail API to extract and structure billing data including invoices, receipts, and payment confirmations.
  \item Implemented OAuth 2.0 authentication and keyword-based filtering, applying security best practices for API access and reducing noise in results.
  \item Handled edge cases including forwarded threads, inconsistent formatting, and duplicates, improving reliability and output quality of the pipeline.
\end{itemize}
\noindent\textbf{Hand Gesture Recognition System} \href{https://github.com/Gogeta0011/Hand-Gestures}{[github]} \textbar\ Python, OpenCV, MediaPipe \hfill July 2025
\begin{itemize}
  \item Built a real-time computer vision pipeline using OpenCV and MediaPipe to detect and classify hand gestures from a live camera feed with low latency.
  \item Tuned detection thresholds and optimized frame processing to reduce false triggers and maintain stable performance across varied lighting and camera distances.
  \item Mapped gesture outputs to system actions, demonstrating end-to-end integration from sensor input to application-level response.
\end{itemize}

%--- Education ---%
\section{EDUCATION}
\textbf{Bachelor of Technology (B.Tech) in Computer Science and Engineering (CSE)} \hfill Graduated June 2025\\
Jawaharlal Nehru Technological University, Hyderabad \hfill Telangana, India\\
\textbf{Relevant Coursework:} Cloud Computing, Operating Systems, Computer Networks, Software Engineering, Database Management Systems, Data Structures \& Algorithms

\end{document}
